Cosmological constraints from the redshift dependence of the volume effect: galaxy angular 2-point correlation function

### 2017-04-01 draft/draft3.tex
updates

The outline of this paper proceeds as follows. 
In \S 2 we briefly review the nature and consequences of the LSS geometric distortion when performing coordinate transforms in a cosmological context. 
In \S 3 we describe the N-body mock galaxies used to test our method.
The methodology is presented in \S 4.
We conclude in \S 5.

@@

The mis-scaling not only changes the shape of the 2pCF but also modifies its amplitude. %The amplitude of $r_\perp\omega$ is amplified due to the stretch of scale.
As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
the higher the redshift, the greater the enhancement.%the amplitude monotonically increases as a function of redshift.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
   \includegraphics[width=8cm]{fig9_a.eps}
   \includegraphics[width=8cm]{fig9_b.eps}
   }
   \caption{\label{fig_contours}
   Left: Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
   based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
   Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
   the method can lead to very tight cosmological constraint.
   Right: The constraints in case that one or two high redshift bins are not used. 
   }
\end{figure*}

@@

In summary, the effect of RSD and galaxy bias on the shape of galaxy angular correlation function is, not large, but it is still non-negligible.
When dealing with real observational data, one should construct simulation mocks in which these effects are reliably modelled, 
so that the systematics are corrected and will not lead to significant bias in the derived cosmological constraints.

@@

@@

In case that we do not have high redshfit galaxies, the constraint becomes weaker.
Figure \ref{fig_contours} displays that, 
in case that we only use the galaxies at $z=$0, 0.5 and 1, 
the 2$\sigma$ uncertainties of $\delta\Omega_m\approx0.01,\\ \delta w\approx0.1$ (the other parameter fixed at its best-fit value).
The area of contour is further enlarged by $\approx 50\%$ if we only use galaxies at $z=$0 and 0.5.

>>>>

The outline of this paper proceeds as follows. 
In \S 2 we briefly review the nature and consequences of the LSS geometric distortion when performing coordinate transforms in a cosmological context. 
In \S 3 we describe the N-body mock galaxies used to test our method.
The methodology is presented in \S 4.
The cosmological constraints from the method is presented in \S 5.
We conclude in \S 6.

@@

The mis-scaling not only changes the shape of the 2pCF but also changes the value of the $y$-axis
\footnote{}. %The amplitude of $r_\perp\omega$ is amplified due to the stretch of scale.
As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
the higher the redshift, the greater the enhancement.%the amplitude monotonically increases as a function of redshift.

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=7cm]{Tpcf--contour.eps}
   %\includegraphics[width=16cm]{Tpcf--contour-others.eps}
   %\includegraphics[width=16cm,natwidth=52,natheight=40]{fig10.eps}
   \includegraphics[width=8cm]{fig9_a.eps}
   \includegraphics[width=8cm]{fig9_b.eps}
   }
   \caption{\label{fig_contours}
   Left: Likelihood contours (68.3\%, 95.4\%) in the $\Omega_m-w$ plane from our method, 
   based on the redshift evolution of the angular 2pCF shape $\hat\omega_{r_\perp}$.
   The green point denotes our fiducial cosmological model and the contours denote the statistical error.
   Utilizing the HR4 snapshots data of mock galaxies at five redshifts,
   the method lead to very tight cosmological constraint.
   Right: The constraints in case that one or two high redshift bins are not used. 
   }
\end{figure*}

@@

%In summary, the effect of RSD and galaxy bias on the shape of galaxy angular correlation function is, not large, but it is still non-negligible.
%When dealing with real observational data, one should construct simulation mocks in which these effects are reliably modelled, 
%so that the systematics are corrected and will not lead to significant bias in the derived cosmological constraints.

@@

\subsubsection{More discussion}

In summary, we aim to minimise the redshift evolution of the shape of the normalised angular 2pcf; 
the shape change is dramatic when considering a cosmology much deviated from the fiducial model.
However even in the case of the correct cosmology there remains a small signal, due to growth of structures, RSD and galaxy bias. 
These systematics are removed with the aid of simulations.
The procedure of the correction of systematics is similar to what was implemented in our previous papers \cite{Li2014,Li2015,Li2016}.

The systematics are estimated from a simulation conducted using a particular cosmology. 
There could be a bias in the estimation if the simulation cosmology is different from the truth. 
The bias would not be serious if the simulation cosmology turns out to be consistent with the best-fit cosmological parameters obtained from the analysis \cite{Li2016}. 
In the case that there is a large discrepancy between the simulation cosmology and the best-fit cosmology, one needs to adjust the simulation cosmology and re-do the analysis.

A more precise approach would involve estimating the systematic effect from a set of simulations covering the relevant volume of the parameter space. 
This would remove the remaining uncertainty associated with the cosmological dependence. 
This approach would also enable the estimation of the $systematics\ errors$, 
which could be important when the sample size is large enough and the $systematic\ error$ becomes as small as the $statistical\ error$.

The third row of Figure \ref{fig_sys} shows that, 
if having a large difference in bias between the samples,
there is a large systematic variation on small scales. 
This means that an accurate modelling of systematics from simulations is required. 
To avoid the possible difficulty, one can conduct the analysis using a volume-limited sample, 
where the redshift evolution of galaxy properties is small and the systematic effect from RSD and galaxy bias is also small,
as shown by the fourth row of Figure \ref{fig_sys}.

To avoid the large systematics in the nonlinear regime, 
another solution would be to increase the scale of analysis to larger separations where the non-linear effect is becoming subdominant. 
Figure \ref{fig_sys} shows that, 
on scales of $s=20-50 h^{-1} {\rm Mpc}$ the systematic effect is 2-3 times smaller than that of $s=5-20 h^{-1} {\rm Mpc}$. 
Actually, we tested and found that, using $s = 5-40 h^{-1} {\rm Mpc}$ and $20-40 h^{-1} {\rm Mpc}$, 
yields cosmological constraints that are pretty close to each other (see \S 4).

We do not consider the systematic effects in case of non-standard cosmological scenarios such as modified gravity and warm dark energy. 
These topics go beyond the scope of this work, and they are worthy future investigations.

@@

In case that we do not have high redshift galaxies, the constraint becomes weaker.
The upper-right panel of Figure \ref{fig_contours} displays that, 
in case that we only use the galaxies at $z=$0, 0.5 and 1, 
the 2$\sigma$ uncertainties of $\delta\Omega_m\approx0.01,\\ \delta w\approx0.1$ (the other parameter fixed at its best-fit value).
The area of contour is further enlarged by $\approx 50\%$ if we only use galaxies at $z=$0 and 0.5.

So far we simply follow the convention of \cite{Li2016} and adopts $5\hMpc <s< 40\hMpc$. 
As discussed in the \S 4.3.3, one may want to avoid large systematics in the non-linear regime. 
In this case one can adopt $20\hMpc<s<40\hMpc$,
which significantly reduces the systematic effects while not much weaken the power of the final constraints,
as shown by the lower-left panel of Figure \ref{fig_contours}.

The choice of the redshift width $105 \hMpc$ is also slightly little arbitrary. 
It should be larger than the distance distortion from the RSD and redshift errors.
The optimistic scheme of clustering scales and redshift width should depend on the specific galaxy sample used in the analysis. 
One could adjust them to have a good balance between the power of cosmological constraint and the size of systematic effect.
